\flushleft
\textbf{Objectives of the Study}\\
\justifying
\parx
The general objective of the study is to develop a CodeNect: Visual Programming
Software that will help in learning the fundamentals of programming.

\parx
Specifically, this study seeks:

\begin{enumerate}
	\item Identify the concepts learners find difficult to understand through conducted survey.
	\item Analyze the problems through data gathering.
	\item Design the system with the following modules:
		\begin{enumerate}
			\item Visual Nodes Module handles the core elements and building blocks
				in the software for writing logic and code.
			\item Filesystem Module handles the creation, modification, reading, and
				deletion of files.
			\item Input and Output Module is the interface for user actions such as mouse
				events and key events and what is displayed to the screen for the user.
			\item Debug Module lints the visual code for errors and warnings before
				the running the code. It also captures errors and warnings during runtime
				and report it to the user.
			\item Simulation Module for compiling and running the visual program to
				a command line program.
			\item Transpiler Module that will convert the visual logic to the
				C programming language.
			\item Assessment Module that will evaluate the knowledge and learning of the
				users by providing basic and common coding exercises. Exercises can be
				imported, shared, and distributed through simple package files.
		\end{enumerate}

	\item Develop the system as designed using the C++ programming language,
		GLFW and OpenGL renderers, TinyC Compiler as runtime compiler and runner,
		and DearImGui and ImNodes as user-interface libraries.
	\item Test and improve the usability and functionality of the software using metrics.
	\item Evaluate the acceptability of the software using the ISO 9126. \\
\end{enumerate}
