\flushleft
\textbf{Summary}
\justifying

\parx
The study is the development of a visual programming software for aiding
beginners in the field of programming get a better grasp and understanding
about its fundamentals.  The software "CodeNect: Visual Programming Software
for Learning Fundamentals of Programming" was developed with the purpose of
aiding beginners in learning the fundamentals of programming in the field of
technology and to serve as an intermediary software in helping beginners get
familiarized with programming.

\parx
The gathering of data needed for the studies was achieved through the
conduction of survey, review of existing related studies and journals, and
research on the Internet.

\parx
The software is composed of seven modules which are the Input/Output, Visual
Nodes, Transpiler, Filesystem, Simulation, Debug, and Assessment modules. The
software was developed using the C++ programming language and the usage of
multiple open-source libraries for graphics and tools. TinyC Compiler was used
for compiling and running the transpiled C code at runtime. Adobe Photoshop
and Aseprite were used for the icons and logo.

\parx
The V-Model was used as methodology for the development of the software which
has the following phases: requirements, system design, architecture design, module
design, implementation and coding, and testing.

\parx
The software was evaluated of its features and functionalities using the ISO
9126. The remarks and verification by ten college students taking programming
subjects as non-technical evaluators and another ten IT professionals as technical
evaluators.

% TODO add at the end the result of evaluation
