\begin{doublespace}
	\thispagestyle{empty}

	\begin{center}
		\textbf{ACKNOWLEDGMENT}
	\end{center}
	\leavevmode\\

	\justify
	\parx
	The researchers express their gratitude and earnest appreciation to the
	following people who inspired, helped, and contributed to the development
	and completion of this study:

	\parx
	First and foremost, to God and the Lord and Savior Jesus Christ for the
	boundless grace, knowledge, wisdom, and strength He bestowed continually.
	Our source of strength and hope every time, especially in times we feel
	like giving up.

	\parx
	Mr. James Angelo V. Aves, our thesis adviser, for the advises and supervision
	in the documentation and development of this study.

	\parx
	Ms. Anabelle J. Almarez, our technical critic, for her critics and guidance
	in the documentation and development of this study.

	\parx
	Ms. Gladys G. Perey, unit research coordinator, for her commitment and management
	of the time and schedule for thesis.

	\parx
	Mr. Marlon R. Pereña, department chairman, for his kindness in inspiring and
	assisting the students.

	\parx
	Family, relatives, and church family, for the moral, spiritual, and financial
	support. Our inspiration and motivation that keep us pursuing our dreams.

	\parx
	To the people and fellow programmers in the Löve Discord community, for their
	help and guidance during the development of the software.

	\parx
	This study is sincerely dedicated to all of them and more.

	\null\hfill \textbf{THE RESEARCHERS}
\end{doublespace}
