% \fakesubsection{ISO 9126 Software Engineering - Product Quality}
\flushleft
\textbf{ISO 9126 Software Engineering - Product Quality}\\
\justifying

\parx
The ISO 9126 Software Engineering - Product Quality is a a set of standards for
software testing internationally recognized and approved. Its goal is to
address well known biases of human that has an effect on the delivery and
perception of a software project. This standard defines the following for usage
with software development lifecycle: maintanability, efficiency, portability,
reliability, functionality, and usability of the software product (\cite{iso_9126}).

\parx
\textbf{Functionality}
\justifying
The functionality subset of quality has the following attributes: suitability,
accuracy, interoperability, security, and functionality compliance. These functions
are provided to satisfy and meet the needs.

\parx
\textbf{Reliability}
\justifying
The reliability subset of quality has the following attributes: maturity, fault tolerance,
recoverability, and reliability compliance. It focuses on the capability of the product
in maintaining its performance and quality under light or stress conditions for a period
of time.

\parx
\textbf{Usability}
\justifying
The usability subset of quality has the following attributes: understandability, learnability,
operability, attractiveness, and usability compliance. These adheres to the difficulty and
ease of an individual that must exert and face when using and operating the product.

\parx
\textbf{Efficiency}
\justifying
The efficiency subset of quality has the following attributes: time behaviour, resource
utilization, and efficiency compliance. These attributes refer to the relation between
the performance of the software and the amount of resources used in conditions.

\parx
\textbf{Maintainability}
\justifying
The maintanability subset of quality has the following attributes: analyzability,
changeability, stability, testability, and maintanability compliance. These refer to
the effort required to make adjustments and modifications to the product.

\parx
\textbf{Portability}
\justifying
The portability subset of quality has the following attributes: adaptability,
installability, co-existence, replaceability, and portability compliance. These
characterize the ability of the product to be used or ported from across multiple
environments.
